A multi-dimensional extension of the Lightweight Temporary Compression method

### 2018-09-30 paper.tex

% packages
\usepackage{algorithm}
\usepackage{algorithmic}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\usepackage{amsfonts} % for R symbol (the set of real numbers)
\usepackage{color}
\usepackage[pdftex]{graphicx}
\usepackage{graphicx}
\usepackage[bookmarks=false]{hyperref}
\hypersetup{colorlinks=true,linkcolor=black,citecolor=black,filecolor=black,urlcolor=blue}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{stmaryrd} % for llbracket and rrbracket
\usepackage{subcaption}
\usepackage{nicefrac}
\usepackage{amsmath}
\usepackage{amssymb}
\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\DeclarePairedDelimiter{\floor}{\lfloor}{\rfloor}

@@

\section{Results}
\todo{ result table ?}
\subsection{Data sets}
\todo{ my data set}

@@

\section*{Acknowledgement}

>>>>

% packages
\usepackage{algorithm}
\usepackage{algorithmic}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
%\usepackage{algpseudocode}

\usepackage{amsfonts} % for R symbol (the set of real numbers)
\usepackage{color}
\usepackage[pdftex]{graphicx}
\usepackage{graphicx}
\usepackage[bookmarks=false]{hyperref}
\hypersetup{colorlinks=true,linkcolor=black,citecolor=black,filecolor=black,urlcolor=blue}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{stmaryrd} % for llbracket and rrbracket
\usepackage{subcaption}
\usepackage{nicefrac}
\usepackage{amsmath}
\usepackage{amssymb}
\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\DeclarePairedDelimiter{\floor}{\lfloor}{\rfloor}

@@

\section{Results}
\todo{ result table ?}
\subsection{Experiment 1: Pilot tests on Computer}
\begin{itemize}
    \item Data set: 5-times bicep curl which includes 613 data; 
                    Mohammad Lateral bicep curl which include 41428 data; 
                    All data is collected from Neblina, with 50Hz sampling of Sensors.
    \item Experiment Condition: Fedora 64-bit system with 16G memory, i5-3210M CPU @ 2.50GHz × 4. For each data set, we change number of Dimension and EPSILON.
    \item Result: Result shows in table.
    \item Conclution: 
\end{itemize}

\subsection{Experiment 1: energy reduction on the Neblina}
\begin{itemize}
    \item Data set: 5-times bicep curl which includes 613 data; 
                    Mohammad Lateral bicep curl which include 41428 data; 
                    All data is collected from Neblina, with 50Hz sampling of Sensors.
    \item Experiment Condition: Fedora 64-bit system with 16G memory, i5-3210M CPU @ 2.50GHz × 4. For each data set, we change number of Dimension and EPSILON.
    \item Result: Result shows in table.
    \item Conclution: 
\end{itemize}

\section{Implementation}
Our code is available at ... (make a clean release!)

\subsection{Multidimensional LTC with Manhattan distance}
In practice, Multidimensional LTC is same as implementing LTC in each parameter respectively. But we did some changes in our method. Assume $(x_{i1}, x_{i2}, ..., x_{in},t_i)$ is the $i_{th}$ coming data with n-dimension, and a base data point Z  $(z_{1}, z_{2}, ..., z_{n},t_z)$~\cite{schoellhammer2004lightweight}. We map each coming data to $t_1$ time-stamp and create a bounding box for recording overlapping range which includes upper and lower bound for each dimension base on $t_1$. cause the time different between two adjacent data, so the $i_th$ data after mapping is $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$. After that updating tolerance range by adding designed error margin which after mapping $\frac{\epsilon}{t_i-t_z}$ on $\hat{x_{ij}}, j={1...n}$ with Manhattan distance. checking if there is overlap between tolerance and bounding box.The algorithm is as follows.
\note{not clear about Manhattan distance, in my opinion for each axis the distance less than $EPSILEN/t_i-t_0$ + bounding box length}

\section{Results}
\todo{ result table ?}
\subsection{Data sets}
\todo{ my data set}
>>>>>>> f097356e5357084561a03d31cfda480c342f78a7

@@

\section*{Acknowledgement}
\begin{table}[]
    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
    \hline
    \multicolumn{9}{|l|}{Dimension 2}                                                                                                                         \\ \hline
    Dataset                & \multicolumn{4}{l|}{5-times bicep curl}                        & \multicolumn{4}{l|}{Mohammad Lateral bicep}                     \\ \hline
    Distance               & \multicolumn{2}{l|}{Manhattan} & \multicolumn{2}{l|}{Eclidean} & \multicolumn{2}{l|}{Manhattan} & \multicolumn{2}{l|}{Euclidean} \\ \hline
    Epsilon                & 100          & 100/sqrt(2)     & 100         & 100/sqrt(2)     & 100        & 100/sqrt(2)       & 100        & 100/sqrt(2)       \\ \hline
    Max Error              & 127.63       & 94.46           & 99.63       & =               & =          & =                 & =          & =                 \\ \hline
    Compression Radio      & 29.03\%      & 20.88\%         & 25.12\%     & =               & =          & =                 & =          & =                 \\ \hline
    Max memory Usage(heap) & 80B          & 80B             & 648B        & =               & =          & =                 & =          & =                 \\ \hline
    processing time Usage  & 0.005        & 0.005           & 0.005       & =               & =          & =                 & =          & =                 \\ \hline
    \end{tabular}
\end{table}

\begin{table}[]
    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
    \hline
    \multicolumn{9}{|l|}{Dimension 3}                                                                                                                         \\ \hline
    Dataset                & \multicolumn{4}{l|}{5-times bicep curl}                        & \multicolumn{4}{l|}{Mohammad Lateral bicep}                     \\ \hline
    Distance               & \multicolumn{2}{l|}{Manhattan} & \multicolumn{2}{l|}{Eclidean} & \multicolumn{2}{l|}{Manhattan} & \multicolumn{2}{l|}{Euclidean} \\ \hline
    Epsilon                & 100          & 100/sqrt(3)     & 100         & 100/sqrt(3)     & 100        & 100/sqrt(3)       & 100        & 100/sqrt(3)       \\ \hline
    Max Error              & 127.63       & 94.46           & 99.63       & =               & =          & =                 & =          & =                 \\ \hline
    Compression Radio      & 29.03\%      & 20.88\%         & 25.12\%     & =               & =          & =                 & =          & =                 \\ \hline
    Max memory Usage(heap) & 80B          & 80B             & 648B        & =               & =          & =                 & =          & =                 \\ \hline
    processing time Usage  & 0.005        & 0.005           & 0.005       & =               & =          & =                 & =          & =                 \\ \hline
    \end{tabular}
\end{table}
